---
title: "Case Study 2"
author: "Fabio"
date: "8/2/2019"
output: 
   html_document:
    toc: TRUE
    toc_float:
      collapsed: true
      smooth_scroll: false
    theme: paper
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = F)
knitr::opts_chunk$set(message = F)
```


```{r, echo= TRUE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(reshape2)
library(tidyverse)
library(stringr)
library(caret)
library(fpp2)
library(dygraphs)
library(xts)
library(pander)
library(purrr)
library(ggthemes)
library(gridExtra)
library(cowplot)
library(RColorBrewer)
library(gplots)
library(corrplot) 
library(functional)
library(fastNaiveBayes)
library(ggpubr)
```

### Loading the data
```{r, echo= TRUE}
dfdata<- readr::read_csv("CaseStudy2-data.csv")
head(dfdata)
```


#### Atrittion calculation

```{r, echo= TRUE}
dfdata %>% count(Attrition) ->att
att
```




### Exploratory plot for Attrition

You can also embed plots, for example:

```{r, echo= TRUE}
agePlot <- ggplot(dfdata,aes(Age,fill=Attrition))+geom_density()+theme_tufte()+scale_fill_few("Medium") #maybe
agePlot
travelPlot <- ggplot(dfdata,aes(BusinessTravel,fill=Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium")
travelPlot
ratePlot <- ggplot(dfdata,aes(DailyRate, fill = Attrition))+geom_density()+theme_tufte()+scale_fill_few("Medium")
ratePlot
depPlot <- ggplot(dfdata,aes(Department,fill = Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium")
depPlot
distPlot<- ggplot(dfdata,aes(DistanceFromHome,fill=Attrition))+geom_density()+theme_tufte()+scale_fill_few("Medium") # important
distPlot
eduPlot <- ggplot(dfdata,aes(Education,fill=Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium") #maybe
eduPlot
edufieldPlot <- ggplot(dfdata,aes(EducationField,fill=Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium")# important
edufieldPlot
envPlot <- ggplot(dfdata,aes(EnvironmentSatisfaction,fill=Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium")# maybe
envPlot
genPlot <- ggplot(dfdata,aes(Gender,fill=Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium") #maybe
genPlot
hourlyPlot <- ggplot(dfdata,aes(HourlyRate,fill=Attrition))+geom_density()+theme_tufte()+scale_fill_few("Medium") #maybe
hourlyPlot
jobInvPlot <- ggplot(dfdata,aes(JobInvolvement,fill=Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium") #important
jobInvPlot
jobLevelPlot <- ggplot(dfdata,aes(JobLevel,fill=Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium") # important
jobLevelPlot
jobSatPlot <- ggplot(dfdata,aes(JobSatisfaction,fill=Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium") # important
jobSatPlot
overTimePlot <- ggplot(dfdata,aes(OverTime,fill=Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium") # important
overTimePlot
hikePlot <- ggplot(dfdata,aes(PercentSalaryHike, fill = Attrition))+geom_density()+theme_tufte()+scale_fill_few("Medium")# important
hikePlot
perfPlot <- ggplot(dfdata,aes(PerformanceRating,fill = Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium")# maybe
perfPlot
RelSatPlot <- ggplot(dfdata,aes(RelationshipSatisfaction,fill = Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium")# important
RelSatPlot
StockPlot <- ggplot(dfdata,aes(StockOptionLevel,fill = Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium")# important
StockPlot
workingYearsPlot <- ggplot(dfdata,aes(TotalWorkingYears,fill = Attrition))+geom_density()+theme_tufte()+scale_fill_few("Medium")# important
workingYearsPlot
TrainTimesPlot <- ggplot(dfdata,aes(TrainingTimesLastYear,fill = Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium")
TrainTimesPlot
 WLBPlot<- ggplot(dfdata,aes(WorkLifeBalance,fill = Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium")# important
  WLBPlot
marPlot <- ggplot(dfdata,aes(MaritalStatus,fill=Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium")#maybe
marPlot
monthlyIncPlot <- ggplot(dfdata,aes(MonthlyIncome,fill=Attrition))+geom_density()+theme_tufte()+scale_fill_few("Medium")# important
monthlyIncPlot
monthlyRatePlot <- ggplot(dfdata,aes(MonthlyRate,fill=Attrition))+geom_density()+theme_tufte()+scale_fill_few("Medium")
monthlyRatePlot
numCompPlot <- ggplot(dfdata,aes(NumCompaniesWorked,fill=Attrition))+geom_density()+theme_tufte()+scale_fill_few("Medium") # important
numCompPlot
YearAtComPlot <- ggplot(dfdata,aes(YearsAtCompany,fill = Attrition))+geom_density()+theme_tufte()+scale_fill_few("Medium") # important
YearAtComPlot
YearInCurrPlot <- ggplot(dfdata,aes(YearsInCurrentRole,fill = Attrition))+geom_bar()+theme_tufte()+scale_fill_few("Medium")
YearInCurrPlot
YearsSinceProm <- ggplot(dfdata,aes(YearsSinceLastPromotion,fill = Attrition))+geom_density()+theme_tufte()+scale_fill_few("Medium") #maybe
YearsSinceProm 
YearsCurrManPlot <- ggplot(dfdata,aes(YearsWithCurrManager,fill = Attrition))+geom_density()+theme_tufte()+scale_fill_few("Medium") # important
YearsCurrManPlot

```
```{r, echo= TRUE}
myplot <- ggplot(dfdata, aes(BusinessTravel, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot

myplot <- ggplot(dfdata, aes(Department, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot

myplot <- ggplot(dfdata, aes(Education, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot

myplot <- ggplot(dfdata, aes(EducationField, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot

myplot <- ggplot(dfdata, aes(EnvironmentSatisfaction, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot # maybe
myplot <- ggplot(dfdata, aes(Gender, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot

myplot <- ggplot(dfdata, aes(JobInvolvement, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot

myplot <- ggplot(dfdata, aes(JobLevel, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot # important

myplot <- ggplot(dfdata, aes(JobSatisfaction, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot

myplot <- ggplot(dfdata, aes(OverTime, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot # important

myplot <- ggplot(dfdata, aes(RelationshipSatisfaction, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot

myplot <- ggplot(dfdata, aes(StockOptionLevel, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot # important

myplot <- ggplot(dfdata, aes(WorkLifeBalance, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot

myplot <- ggplot(dfdata, aes(MaritalStatus, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot # maybe

myplot <- ggplot(dfdata, aes(YearsInCurrentRole, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot #maybe

myplot <- ggplot(dfdata, aes(YearsWithCurrManager, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot # important

myplot <- ggplot(dfdata, aes(YearsAtCompany, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot # important/maybe

myplot <- ggplot(dfdata, aes(NumCompaniesWorked, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot

myplot <- ggplot(dfdata, aes(TrainingTimesLastYear, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot

myplot <- ggplot(dfdata, aes(TotalWorkingYears, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot # maybe

myplot <- ggplot(dfdata, aes(DistanceFromHome, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot # maybe

myplot <- ggplot(dfdata, aes(Age, group = Attrition)) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~Attrition)

myplot



myplot <- ggplot(dfdata, aes(EducationField, group = JobSatisfaction )) + 
          geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          ylab("relative frequencies") +
          facet_grid(~JobSatisfaction)

myplot

```


### Ecploratory plot for Montly income. This is with numerical values

```{r, echo= TRUE}
ys <- names(dfdata)[c(2, 5, 7, 14, 20, 21, 22, 25, 30, 31, 33, 34, 35, 36)]
ys %>% map(function(y) 
  ggplot(dfdata , aes(MonthlyIncome)) + geom_point(aes_string(y=y)))

```
#### More exploratory data for montly income with heatmap for numerical values


```{r, echo= TRUE}
dfn <-dfdata[c(2, 5, 7, 14, 20, 21, 22, 25, 30, 31, 33, 34, 35, 36 )]

my_palette <- colorRampPalette(c("red", "white", "black"))
heatmapper <- function(df){
  df %>%
    keep(is.numeric) %>%
    tidyr::drop_na() %>%
    cor %>%
    heatmap.2(col = my_palette ,
              density.info = "none", trace = "none",
              dendogram = c("both"), symm = F,
              symkey = T, symbreaks = T, scale = "none",
              key = T)
}


heatmapper(dfn)
```

#### More exploratory data for montly income with corrplot for numerical values

```{r, echo= TRUE}
correlator  <-  function(df){
  df %>%
    keep(is.numeric) %>%
    tidyr::drop_na() %>%
    cor %>%
    corrplot( addCoef.col = "white", number.digits = 2,
              number.cex = 0.5, method="square",
              order="hclust", title="Variable Corr Heatmap",
              tl.srt=45, tl.cex = 0.8)
}

correlator(dfn)
```
#### More exploratory data for montly income with ggplot numeric for numerical values 

```{r, echo= TRUE}
plotAllNumeric <- function(df){
  df%>%keep(is.numeric) %>%
    gather() %>%
    ggplot(aes(value)) +
    facet_wrap(~ key, scales = "free") +
    geom_density()+geom_histogram() + theme_fivethirtyeight()
}


plotAllNumeric(dfn)
```

#### More exploratory data for montly income for categorical values

```{r, echo= TRUE}
dfdata %>% keep(is.factor) %>% names -> label
ggplot(data = dfdata, aes(x = BusinessTravel, y = MonthlyIncome, fill =BusinessTravel )) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few()
ggplot(data = dfdata, aes(x = Department, y = MonthlyIncome, fill = Department)) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few()
ggplot(data = dfdata, aes(x = as.factor(Education), y = MonthlyIncome, fill = as.factor(Education))) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few() # important
ggplot(data = dfdata, aes(x = EducationField, y = MonthlyIncome, fill = EducationField)) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few()
ggplot(data = dfdata, aes(x = as.factor(EnvironmentSatisfaction), y = MonthlyIncome, fill = as.factor(EnvironmentSatisfaction))) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few()
ggplot(data = dfdata, aes(x = Gender, y = MonthlyIncome, fill = Gender)) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few()
ggplot(data = dfdata, aes(x = as.factor(JobInvolvement), y = MonthlyIncome, fill = as.factor(JobInvolvement))) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few()
ggplot(data = dfdata, aes(x = as.factor(JobLevel), y = MonthlyIncome, fill = as.factor(JobLevel))) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few() # important
ggplot(data = dfdata, aes(x = JobRole, y = MonthlyIncome, fill = JobRole)) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few()# important
ggplot(data = dfdata, aes(x = as.factor(JobSatisfaction), y = MonthlyIncome, fill = as.factor(JobSatisfaction))) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few()
ggplot(data = dfdata, aes(x = MaritalStatus, y = MonthlyIncome, fill = MaritalStatus)) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few()
ggplot(data = dfdata, aes(x = OverTime, y = MonthlyIncome, fill = OverTime)) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few()
ggplot(data = dfdata, aes(x = as.factor(PerformanceRating), y = MonthlyIncome, fill = as.factor(PerformanceRating))) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few() #maybe
ggplot(data = dfdata, aes(x = as.factor(RelationshipSatisfaction), y = MonthlyIncome, fill = as.factor(RelationshipSatisfaction))) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few()
ggplot(data = dfdata, aes(x = as.factor(StockOptionLevel), y = MonthlyIncome, fill = as.factor(StockOptionLevel))) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few() # maybe
ggplot(data = dfdata, aes(x = as.factor(WorkLifeBalance), y = MonthlyIncome, fill =as.factor(WorkLifeBalance))) + geom_boxplot() + scale_fill_few(palette = "Dark") + theme_few()
```


### Cutting the variables for the dataframe that will be used in the model, witht the intention to have better performance of the model.

```{r, echo= TRUE}
dfdata$YearsInCurrentRole<- cut(as.numeric(dfdata$YearsInCurrentRole), breaks = c(-1,1,100))
dfdata$TotalWorkingYears<- cut(as.numeric(dfdata$TotalWorkingYears), breaks = c(-1,1,100))
dfdata$YearsWithCurrManager<- cut(as.numeric(dfdata$YearsWithCurrManager), breaks = c(-1,1,100))
dfdata %>% filter(MaritalStatus %in% c("Single", "Divorce"))-> MaritalStatus
dfdata$MaritalStatus <- as.factor(dfdata$MaritalStatus)
levels(dfdata$MaritalStatus) <- c("NotMarried", "Married", "NotMarried")

```

### Stting the dataframe for the model. After a lot of trial, this was the best model for attrition, we used Naive base model.

```{r, echo= TRUE}
clasy<- dfdata[c("Attrition", "StockOptionLevel", "JobLevel", "MonthlyIncome", "OverTime")]

clasy[c("Attrition","StockOptionLevel", "JobLevel", "OverTime")] <- lapply(clasy[c("Attrition","StockOptionLevel", "JobLevel", "OverTime")], as.factor)
head(clasy)
```

### Split the train and test data

```{r, echo= TRUE}
set.seed(3033)
split <- function(df, p = 0.75, list = FALSE, ...) {
  train_ind <- createDataPartition(df[[1]], p = p, list = list)
  cat("creating training dataset...\n")
  training <<- df[train_ind, ]
  cat("completed training dataset, creating test set\n")
  test <<- df[-train_ind, ]
  cat("done")
}

split(clasy)
```

### We run the Naive bayes model
```{r, echo= TRUE}
library(doParallel)
numcores <- parallel::detectCores() - 1
cl <- makePSOCKcluster(numcores)
registerDoParallel(cl)


set.seed(3333)
trainMethod <- trainControl( method = "repeatedcv", number = 25, repeats = 5, summaryFunction = twoClassSummary, classProbs = TRUE)

fit.nb1 <- train(Attrition ~ .,  data = training, method = "nb", metric = "Spec", trControl = trainMethod)

fit.nb1

plot(fit.nb1)
```

### Sensitivity : 0.7473          
### Specificity : 0.6857
### Accuracy : 0.7373
```{r, echo= TRUE}
test_pred <- predict(fit.nb1, newdata = test)
test_pred
confusionMatrix(test_pred, test$Attrition)
stopCluster(cl)
```


### The top three variables related to Atrittion are the folloeing =  over time, monthly income, and stockoption level.I got this conclusion after the visualization of the data above, the trial and error in the model and this forest mean decreased accuracy.

```{r, echo= TRUE}
library(randomForest)
randomForest(Attrition ~ ., data = clasy, importance = TRUE,
             ntree=2000)-> forest1
varImpPlot(forest1)

```


### Setting the dataframe for monthly income, we will use regression.

```{r, echo= TRUE}
dfdata<- readr::read_csv("CaseStudy2-data.csv")
reg <- dfdata[c("TotalWorkingYears", "YearsAtCompany", "Age", "Education", "JobLevel", "JobRole", "MonthlyIncome", "PerformanceRating", "StockOptionLevel" )]

reg[c("Education","JobLevel", "JobRole","PerformanceRating", "StockOptionLevel")] <- lapply(reg[c("Education","JobLevel", "JobRole","PerformanceRating", "StockOptionLevel")], as.factor)

reg
```

### Train and test split

```{r, echo= TRUE}
set.seed(3033)
split <- function(df, p = 0.75, list = FALSE, ...) {
  train_ind <- createDataPartition(df[[1]], p = p, list = list)
  cat("creating training dataset...\n")
  training <<- df[train_ind, ]
  cat("completed training dataset, creating test set\n")
  test <<- df[-train_ind, ]
  cat("done")
}

split(reg)
```



### After alot of trial and error and review of the visualization above we picked up the best model, which is the one below.
### RMSE = 927.0692

```{r, echo= TRUE}
regincome1 <- lm( MonthlyIncome ~ TotalWorkingYears + JobLevel + JobRole, data  = training)
summary(regincome1)
pred <- predict(regincome1, newdata = test)
str(pred)
ASA2 <- mean((pred[1:nrow(test)] - test$MonthlyIncome)^2)
sqrt(ASA2)
```


### AIC and BIC

```{r, echo= TRUE}
AIC(regincome1)
BIC(regincome1)
```


### We run our model against the test data

```{r, echo= TRUE}
pred2 <- predict(regincome1, newdata = test)
pred2
```



```{r, echo= TRUE}
noinc <- read_csv("CaseStudy2CompSet No Salary (2).csv")
noinc[c("Education","JobLevel", "JobRole","PerformanceRating", "StockOptionLevel")] <- lapply(noinc[c("Education","JobLevel", "JobRole","PerformanceRating", "StockOptionLevel")], as.factor)
noinc
preds <-predict(regincome1, newdata =  noinc)
preddf <- data.frame(predicted = preds, ID = noinc$ID)
preddf <- preddf %>% arrange(ID)
write.csv(preddf, "Case2PredictionsSavorgnanSalary.csv")
```




```{r, echo= TRUE}
library(readr)
noatt <- read_csv("CaseStudy2CompSet No Attrition.csv")
noatt[c("StockOptionLevel", "JobLevel", "OverTime")] <- lapply(noatt[c("StockOptionLevel", "JobLevel", "OverTime")], as.factor)
head(noatt)
```



```{r, echo= TRUE}
test_preda <- predict(fit.nb1, newdata = noatt)
test_preda
predi <- data.frame(predicted = test_preda, ID = noatt$ID)
predited <- predi %>% arrange(ID)


```


```{r, echo= TRUE}

write.csv(predited,"Case2PredictionsSavorgnanAttrition.csv")

```


## Link to the video https://youtu.be/SeucGT5a9gI
```{r, echo= TRUE}


```

